sensiAnPaper1All

### 2015-06-30 sensiAnPaper1All.Rmd
develop analysis

  nScenarios <- 1000
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

  ## save results objects as rda for re-use
  save(listOutMix, file=paste(outFolder,'listOutMix.rda'))

```

>>>>

  nScenarios <- 100
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

  ## save results objects as rda for re-use
  save(listOutMix, file=paste(outFolder,'listOutMix.rda'))
  save(listOutI1, file=paste(outFolder,'listOutI1.rda'))
  save(listOutI2, file=paste(outFolder,'listOutI2.rda'))    
```

### now want to calculate the times to reach critical points and add them on to the input file 
### for different scenarios
### or will sensiPostProc() sort that ?
